### 2013-03-28 doc/sosp13/evaluation.tex
remark on aggregation

\paragraph{Global memory and communication.} We measure the performance of
\Grappa's global memory and communication layers using a faithful
implementation of the giga updates per second (GUPS) benchmark.
Read-modify-write updates are dispatched at random to a large array. This
benchmark stresses the communication layer of \Grappa separately from the
scheduler, because only a single worker is used per system node.
Figure~\ref{fig:grappa-gups} shows that \Grappa is able to sustain well over a
billion updates per second with 64 nodes.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows.}
    \label{fig:grappa-gups}
\end{figure}

>>>>

\paragraph{Global memory and communication.} We measure the performance of
\Grappa's global memory and communication layers using a faithful
implementation of the giga updates per second (GUPs) benchmark.
Read-modify-write updates are dispatched at random to a large array. This
benchmark stresses the communication layer of \Grappa separately from the
scheduler, because only a single worker is used per system node.
Figure~\ref{fig:grappa-gups} shows that \Grappa is able to sustain well over a
billion updates per second with 64 nodes. Note also that when aggregation is turned off, the update rate is flat at the bottom, demonstrating that aggregation is instrumental for good communication performance.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows with and without message aggregation.}
    \label{fig:grappa-gups}
\end{figure}
